Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-23 Papers/ms.tex
Cosmic Horseshoe phone number, and consistency with Dye

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging), although the g-band image is the highest
signal-to-noise of the INT images. Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

@@

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
the SIE family. One way of further investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
Another option which we defer to future work is to implement a more flexible
model (such as a concentric mixture of concentric elliptical lenses).

>>>>

\section{The Cosmic Horseshoe}
As a further demonstration the method, we apply it to the g-band data
of the Cosmic Horseshoe J1004+4112 \citep{belokurov, 2008MNRAS.388..384D} taken with the Isaac Newton Telescope (INT). The image is shown in Figure~\ref{fig:horseshoe_image}.
For this system,
more data is available (i and U band data, as well as more recent
Hubble Space Telescope (HST) imaging), although the g-band image is the highest
signal-to-noise of the INT images. Unfortunately our current implementation
doesn't allow for multi-band data (unlike \citet{2011MNRAS.412.2521B}), and
is quite slow when running on the larger HST image. Therefore this section
should be considered a further demonstration of the technique, and not a
thorough study of this system.

@@

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
the SIE family. One way of further investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
Another option which we defer to future work is to implement a more flexible
model (such as a concentric mixture of concentric elliptical lenses). This
result is consistent with that of \citet{2008MNRAS.388..384D}, who found a slight preference for an elliptical power law profile over the SIE
(which is a specific case of an elliptical power law).
